A Detection of the Environmental Dependence of the Stellar Profiles and Halos of Massive Central Galaxies

### 2017-07-10 draft/paper2.tex
Introduction edits 2

    In \citet[][; Paper I hereafter]{hscMassiveI}, we showed that the deep, 
    multi-band images from the Subaru Strategic Program (SSP; \citealt{HSC_SSP,
    HSC_DR1}) using Hyper Suprime-Cam (HSC; \citealt{Miyazaki2012}, 
    Miyazaki in~prep.) allows us to extract robust surface stellar
    mass density (\mden{}) profiles for {\it individual} massive galaxies 
    at $0.3 < z < 0.5$ out to 100 kpc. 
    In Paper I, we exploited this sensitivity to show that the \mden{} profiles 
    and the shapes of the stellar halos of massive ETGs has a clear \mstar{} 
    dependence. 
    And the fraction of accreted stars residing in the extended envelope increases
    with the total \mstar{} of the galaxy.

    In this paper, we explore how the extended stellar halo in massive central galaxies
    depends on dark matter halo mass with the help of HSC images of a large sample 
    of massive ETGs and the \redm{} cluster catalog (e.g.\ \citealt{Rykoff2014}; 
    \citealt{Rozo2015b}; please see Section~\ref{ssec:redmapper} for details)

    Motivated by the ``two-phase'' scenario, and also due to the difficulty in 
    providing appropriate model to describe the \mstar{} distribution of massive 
    galaxy from its center to the very outskirt, we focus on \mstar{} within two 
    different physical apertures in this work:

@@

    This paper is organized as follows. 
    Section \ref{sec:data} presents our data and our sample selection. 
    Section \ref{sec:ellipse} describes our procedure for extracting 1-D surface 
    brightness profiles. 
    Section \ref{sec:mstar} describes how we estimate stellar mass. 
    Our main results are presented in Section \ref{sec:result} and discussed in 
    Section \ref{sec:discussion}. 
    Section \ref{sec:summary} presents our summary and conclusions.

@@

%% ------------------------------------------------------------------------------------ %% 
\section{Data And Sample Selection}
    \label{sec:data}

%% ------------------------------------------------------------------------------------ %% 
\section{Results}
    \label{sec:results}

>>>>

    In \citet[][Paper I hereafter]{hscMassiveI}, we showed that the deep, 
    multi-band images from the Subaru Strategic Program (SSP; \citealt{HSC-SSP,
    HSC-DR1}) using Hyper Suprime-Cam (HSC; \citealt{Miyazaki2012}, 
    Miyazaki in~prep.) allows us to extract robust surface stellar
    mass density (\mden{}) profiles for {\it individual} massive galaxies 
    at $0.3 < z < 0.5$ out to 100 kpc. 
    In Paper I, we exploited this sensitivity to show that the \mden{} profiles 
    and the shapes of the stellar halos of massive ETGs has a clear \mstar{} 
    dependence. 
    And the fraction of accreted stars residing in the extended envelope increases
    with the total \mstar{} of the galaxy.

    In this paper, we explore how the extended stellar halo in massive central galaxies
    depends on dark matter halo mass with the help of HSC images of a large sample 
    of massive ETGs and the \redm{} cluster catalog (e.g.\ \citealt{Rykoff2014}; 
    \citealt{Rozo2015b}; please see \S \ref{sec:data} for details)

    This paper is organized as follows. 
    \S \ref{sec:data} briefly introduce the sample selection and data reduction 
    processes.  
    Please refer to \citet{hscMassiveI} for more technical details.
    Our main results are presented in \S \ref{sec:result} and discussed in 
    \S \ref{sec:discussion}. 
    \S \ref{sec:summary} presents our summary and conclusions.

    As in \citet{hscMassiveI}, we do not try to separate any potential ``intra-cluster''
    component (ICL; e.g. \citealt{Carlberg1997, Lin2004, Gonzalez2005, Mihos2005}) from 
    massive galaxies in our sample for both technical and scientific reasons.  
%% ------------------------------------------------------------------------------------ %%

%% ------------------------------------------------------------------------------------ %% 
%% Sample Selection and Data Reduction
%% ------------------------------------------------------------------------------------ %% 
\section{Sample Selection and Data Reduction}
    \label{sec:data}

%% ------------------------------------------------------------------------------------ %% 
    Motivated by the two-phase formation scenario, we focus on \mstar{} within two 
    different physical apertures in this work:

@@

@@

%% ------------------------------------------------------------------------------------ %% 
%% Results 
%% ------------------------------------------------------------------------------------ %% 
\section{Results}
    \label{sec:result}
